### 2022-07-07 sections/1-introduction.tex
Some notes, new backronym, some citations

>>>>

- introduce kNN~\cite{fix1952discriminatory, cover1967nearest} as one of the most pervasive supervised classification methods in use
- performance difficulties of naive kNN, and introduce existing improvements such as locality-sensitive hashing~\cite{bingham2001random}
- Introduce Compressed Accelerated K-nearest-neighbor Entropy-scaling Search (CAKES)
% note new backronym (NMD)

### 2022-07-07 sections/5-results.tex
Some notes, new backronym, some citations

Ark: a 28-core Intel Xeon E5-2690 v4 2.60GHz, 512GB RAM and CentOS 7 Linux with kernel 3.10.0-1127.13.1.el7.x86\_64 \#1 SMP. Rust 1.52, Python 3.6.8

Macbook Air: 8-core (4 performance, 4 efficiency) Apple M1 processor with 16GB RAM, macOS 11.3. Rust 1.52, Python 3.9.4

>>>>

Ark: a 28-core Intel Xeon E5-2690 v4 2.60GHz, 512GB RAM and CentOS 7 Linux with kernel 5.15.50-1-MANJARO \#1 SMP PREEMPT. Rust 1.62, Python 3.10.5

Macbook Air: 8-core (4 performance, 4 efficiency) Apple M1 processor with 16GB RAM, macOS 12.1. Rust 1.62, Python 3.9.4
